\bf What is the Best Way to Display Two Time Series to Read Association?

### 2016-02-01 paper/paper.Rnw
citing

The lineup protocol equips exploratory visual methods with a rigorous procedure that enables statistical inference. This is important because visualization remains essential for data analysis because human eyes can detect patterns which would not be detected mathematically. The lineup protocol provides the calibration of the human eyes to prevent us from erroneously jumping to conclusions about magic patterns. Prior to the protocol description, we can find preliminary ideas along these lines, for example \citet{Daniel} recommends looking at plots of data from a null distribution for exploring two factor design experimental data.  His paper provides 40 pages of plots from the null! He encourages data analysts to understand the patterns that might be seen in samples data drawn from populations without inherent structure. (\citep{Buja} has named this the Rorschach protocol.)

@@

>>>>

The lineup protocol equips exploratory visual methods with a rigorous procedure that enables statistical inference. This is important because visualization remains essential for data analysis because human eyes can detect patterns which would not be detected mathematically. The lineup protocol provides the calibration of the human eyes to prevent us from erroneously jumping to conclusions about magic patterns. Prior to the protocol description, we can find preliminary ideas along these lines, for example \citet{Daniel} recommends looking at plots of data from a null distribution for exploring two factor design experimental data.  His paper provides 40 pages of plots from the null! He encourages data analysts to understand the patterns that might be seen in samples data drawn from populations without inherent structure. \citet{Buja} has named this the Rorschach protocol.)

@@

\section{Acknowledgements}

The authors gratefully acknowledge funding from the National Science Foundation Grant DMS \#1007697.

All code required to reproduce this paper can be found at https://github.com/NTomasetti/correlation.
